An introduction to Docker for reproducible research

### 2014-12-01 docker-paper/manuscript.Rmd
commit final revisions on formatting

bibliography: components/references.bib
csl: components/acm-sig-proceedings.csl

@@

One can  share a public copy of the image just created by using the
`Docker push` command, followed by the name of the image using the command:

@@

If a Dockerfile is made available on a public code repository such as
[Github](https://github.com) or [Bitbucket](https://bitbucket.org),
the Hub can automatically build the image whenever a change is made to
the Dockerfile, making the `push` command unnecessary. A user can update
their local image using the `Docker pull <imagename>`, which downloads
any changes that have since been made to the copy of the image on the Hub.

@@

```bash
docker run -d --name db training/postgres
docker run -d -P --link db:db training/webapp python app.py
```
This separates the task for running the database (first line) from
the application used to analyze the data (second line), allowing a more
modular approach to reuse: another researcher could use the same database
container while connecting it to different scripts.

@@

In addition to version managing the Dockerfile, the images themselves are
versioned using a git-like hash system (_e.g._ see `Docker commit`, `docker
push`/`Docker pull`, `docker history`, `docker diff`).  Docker images and
containers have dedicated metadata specifying the date, author, parent
image, and other details (see `Docker inspect`). One can roll back an
image through the layers of history of its construction, then build off
an earlier layer, or roll back changes made interactively in a
container. For instance, here I inspect recent changes made to the
`ubuntu:14.04` image:

>>>>

bibliography: components/references.bib
csl: components/acm-sig-proceedings.csl
citecolor: black
linkcolor: black
urlcolor: black

@@

One can  share a public copy of the image just created by using the
`docker push` command, followed by the name of the image using the command:

@@

If a Dockerfile is made available on a public code repository such as
[Github](https://github.com) or [Bitbucket](https://bitbucket.org),
the Hub can automatically build the image whenever a change is made to
the Dockerfile, making the `push` command unnecessary. A user can update
their local image using the `docker pull <imagename>`, which downloads
any changes that have since been made to the copy of the image on the Hub.

@@

```bash
docker run -d --name db training/postgres
docker run -d -P --link db:db training/webapp \
  python app.py
```
This separates the task for running the database (first line) from
the application used to analyze the data (second line), allowing a more
modular approach to reuse: another researcher could use the same database
container while connecting it to different scripts.

@@

In addition to version managing the Dockerfile, the images themselves are
versioned using a git-like hash system (_e.g._ see `docker commit`, `docker
push`/`docker pull`, `docker history`, `docker diff`).  Docker images and
containers have dedicated metadata specifying the date, author, parent
image, and other details (see `docker inspect`). One can roll back an
image through the layers of history of its construction, then build off
an earlier layer, or roll back changes made interactively in a
container. For instance, here I inspect recent changes made to the
`ubuntu:14.04` image:
